NanoMaLy

### 2015-11-20 paper/pldi16-submission/evaluation.tex
hide UCSD for anonymity

We answer these questions on two sets of known-bad programs, \ie
programs that were rejected by the \ocaml compiler because of a type
error.
%
The first dataset comes from the Spring 2014 undergraduate Programming
Languages course at UC San Diego. 
%
We recorded each interaction with the \ocaml top-level system over the
course of the first three assignments (IRB \#140608), from which we
extracted 4,407 distinct, ill-typed \ocaml programs.
%
The second dataset -- widely used in the literature -- comes from a
similar course at the University of
Washington~\cite{lerner_seminal:_2006}, from which we extracted 284
ill-typed programs.

@@

\paragraph{Results}
\label{sec:results-complexity}
The results of the experiment are summarized in
Figure~\ref{fig:results-complexity}.
%
The average number of single-step reductions per trace is 26 for the
UCSD dataset (27 for the Seminal dataset) with a maximum of 2,744 (659
for Seminal). The average number of jumps per trace is 3 (also 3 for
Seminal) with a maximium of 177 (52 for Seminal). In both datasets at
least 90\% of the traces contain fewer than 10 jumps.
%

>>>>

We answer these questions on two sets of known-bad programs, \ie
programs that were rejected by the \ocaml compiler because of a type
error.
%
The first dataset comes from the Spring 2014 undergraduate Programming
Languages course at our institution.
%
We recorded each interaction with the \ocaml top-level system over the
course of the first three assignments (IRB \# hidden for blind review), % \#140608),
from which we extracted 4,407 distinct, ill-typed \ocaml programs.
%
The second dataset -- widely used in the literature -- comes from a
similar course at the University of
Washington~\cite{lerner_seminal:_2006}, from which we extracted 284
ill-typed programs.

@@

\paragraph{Results}
\label{sec:results-complexity}
The results of the experiment are summarized in
Figure~\ref{fig:results-complexity}.
%
The average number of single-step reductions per trace is 26 for our
dataset (27 for the UW dataset) with a maximum of 2,744 (659 for
UW). The average number of jumps per trace is 3 (also 3 for
UW) with a maximium of 177 (52 for UW). In both datasets at
least 90\% of the traces contain fewer than 10 jumps.
%
